---
title: "IDS 2883 - First-Year Seminar - Student Survey Analysis"
author: "Fall 2023"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: no
  word_document:
    toc: no
urlcolor: blue
---

```{r setup3, include=F, echo=F}
knitr::opts_chunk$set(echo = FALSE)
options(kableExtra.auto_format = FALSE)
require('knitr')
require('dplyr')
require('readxl') 
require('kableExtra')

options(knitr.kable.NA = '')
#setwd("~/Dropbox/USAO/~IDS 1223/Syllabus")
```

\vspace{-20pt}

```{r include=FALSE}
require(dplyr)

likert2int5 = function( example ) {
  data = revalue(example, 
          c("Strongly Disagree"= 0,
            "Disagree" = 1,
            "Neither Agree nor Disagree" = 2,
            "Agree" = 3,
            "Strongly Agree" = 4) )
  as.integer( data)
}


likert2intTime = function( example ) {
  data = revalue(example, 
          c("1-Never"= 1,
            "5-All the time" = 5) )
  as.integer(data)
}

```

# Pre-semester Survey



```{r include=FALSE}
pre = read.csv("pre_semester_F2023 UIC Check.csv")
post = read.csv("post_semester_F2023 UIC Check.csv")
```


```{r}
both = merge(pre, post, by.x="UIC", by.y="UIC")

both = cbind( both, SMMdif = both$SMM.y-both$SMM.x,
                    GMSdif = both$GMS.y-both$GMS.x)
```


```{r}
CMS = paste("CMS", 1:6,".x", sep="")
CAS = paste("CAS", 1:6,".x", sep="")
NEOS = paste("NEOS",1:9,".x",sep="")

CMSy = paste("CMS", 1:6,".y", sep="")
CASy = paste("CAS", 1:6,".y", sep="")
NEOSy = paste("NEOS",1:9,".y",sep="")


CMScompx = apply( both[,CMS], 2, likert2int5)
CMScompy = apply( both[,CMSy], 2, likert2int5)
```

```{r}
myfactor = function(x) factor(x,levels = 0:4)
myfactorTable = function(x) {
  table( myfactor( CMScompx[,4] ) )
}

myfactorTable( CMScompx[,4] )
```

```{r}
Xt = apply( CMScompx, 2, myfactorTable)
lapply(Xt, barplot, las = 2)
```



```{r}
X = apply( CMScompy, 2, table)
lapply(X, barplot, las = 2)
```






## Reliability (Cronbach's Alpha)


```{r}
require(ltm)
a1 = cronbach.alpha( na.omit( GMSpre ) )
a2 = cronbach.alpha( na.omit( GMSpost ) )
a3 = cronbach.alpha( rbind( na.omit( GMSpre ), na.omit( GMSpost ) ))
a = c(a1$alpha,a2$alpha,a3$alpha)
names(a) = c("Pre-semester","Post-semester", "Aggregate")
a
```

## Pre vs Post

Unpaired 

```{r}
par(mfrow = c(1, 2))
hist(pre$GMS, breaks = 5)
hist(post$GMS, breaks = 5)
```

```{r}
t.test(pre$GMS, post$GMS)
```



# SMM




SMMpre  = SMMcomp( pre )
SMM = apply(SMMpre, 1, mean)
pre = cbind(pre, SMM = SMM)

SMMpost = SMMcomp( post )
SMM = apply(SMMpost, 1, mean)
post = cbind(post,SMM = SMM)
```



## Reliability (Cronbach's Alpha)


```{r}
require(ltm)
a1 = cronbach.alpha( na.omit( SMMcomp( pre )) )
a2 = cronbach.alpha( na.omit( SMMcomp( post )) )
a3 = cronbach.alpha( rbind( na.omit( SMMcomp( pre )), na.omit( SMMcomp( post )) ))
a = c(a1$alpha,a2$alpha,a3$alpha)
names(a) = c("Pre-semester","Post-semester", "Aggregate")
a
```


## Pre vs. Post

Unpaired

```{r}
t.test(pre$SMM, post$SMM)
```


```{r}
pre = cbind(pre, SMMpre, GMSpre)
post = cbind(post, SMMpost, GMSpost)
```



# BOTH



```{r}
BOTH = intersect(pre$UIC,post$UIC)

BothPre = c()
for ( i in 1:99) {
  BothPre = c(BothPre, which( pre$UIC==BOTH[i]))
}
BothPost = c()
for ( i in 1:99) {
  BothPost = c(BothPost, which( post$UIC==BOTH[i]))
}

```

```{r}
both = merge(pre, post, by.x="UIC", by.y="UIC")

both = cbind( both, SMMdif = both$SMM.y-both$SMM.x,
                    GMSdif = both$GMS.y-both$GMS.x)
```


```{r}
hist( both$SMM.y - both$SMM.x)
```


```{r}
t.test( both$SMM.y - both$SMM.x, alternative = "greater")
wilcox.test( both$SMM.y - both$SMM.x, alternative = "greater")
```


```{r}
hist( both$GMS.y - both$GMS.x)
```

```{r}
t.test( both$GMS.y - both$GMS.x, alternative = "greater")
wilcox.test( both$GMS.y - both$GMS.x, alternative = "greater")
```


```{r}
names(both)
```

```{r}
both$Grad_4yrs.x
```

```{r}
with(both, t.test( GMS.x, GMS.y, paired = T ))
```
```{r}
with(both, t.test( SMM.x, SMM.y, paired = T ))
```



```{r}
lm1 = lm( Grad_4yrs.y ~ GMSdif + SMMdif + Gender.x, data = both)

summary(lm1)
```

